From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-20 paper.tex
Chronbach`s alpha test results added

    \begin{tabular}{p{5.5cm}cccccccc}
        \toprule
        {\bf Subject} & 1 & 2 & 3 & 4 & 5 & 6 & {\bf Avg.} & {\it SD} \\
        \midrule
        {\bf Head pose tracking} (\%) & 88.2 & 83.5 & 90.5 & 83.1 & 87.9 & 85.0 & {\bf 86.4} & {\it 3.0} \\ 
        \midrule
        {\bf Ground-truth/robot match} (\%) & 61.1 & 85.5 & 80.8 & 62.2 & 63.4 & 83.9 & {\bf 72.8} & {\it 11.7}\\
        {\bf Cronbach's $\alpha$} &  & & & & & & & \\
        {\bf Cosine affinity} & 0.73 & 0.82 & 0.87 & 0.73 & 0.77 & 0.89 & {\bf 0.8} & {\it 0.07} \\
        \bottomrule
    \end{tabular}
    \label{tab:results}
\end{table*}

@@

For instance, subjects 1,4 and 5 despite the fact that the tracking accuracy is
in the average, the bad precision in the captured VFoA suggests that such
children are highly likely to modify the gaze direction without head move
intervention reducing dramatically the overlap between captured and real VFoA.

>>>>

    \begin{tabular}{p{5.5cm}cccccccc}
        \toprule
        {\bf Subject} & 1 & 2 & 3 & 4 & 5 & 6 & {\bf Avg.} & {\it SD} \\
        \midrule
        {\bf Head pose tracking} (\%) & 88.2 & 83.5 & 90.5 & 83.1 & 87.9 & 85.0 & {\bf 86.4} & {\it 3.0} \\ 
        \midrule
        {\bf Ground-truth/robot match} (\%) & 61.1 & 85.5 & 80.8 & 62.2 & 63.4 & 83.9 & {\bf 72.8} & {\it 11.7}\\
        {\bf Cronbach's $\alpha$} & 0.63 & 0.81 & 0.82 & 0.59 & 0.64 & 0.78 & {\bf0.71} & {\it0.10}\\
        {\bf Cosine affinity} & 0.73 & 0.82 & 0.87 & 0.73 & 0.77 & 0.89 & {\bf 0.8} & {\it 0.07} \\
        \bottomrule
    \end{tabular}
    \label{tab:results}
\end{table*}

@@

For instance, subjects 1,4 and 5 despite the fact that the tracking accuracy is
in the average, the bad precision in the captured VFoA suggests that such
children are highly likely to modify the gaze direction without head movement
intervention reducing dramatically the overlap between the manually annotated 
focus of attention and robot's computed focus of attention.
